Deep learning for quality control of surface physiographic fields using satellite Earth observations

### 2023-05-20 docs/submission/template.tex

\noindent It is a continuous enterprise to update the lake parametrization schemes and their input data fields to better represent small-scale surface processes. It is however challenging to accurately represent lakes in these parametrisations; the majority of lakes which are resolved at a 9km grid spacing have not had their morphology accurately measured, let alone monitored, whilst 28.9$\%$ of land and coastal cells are treated for sub-grid (i.e. covering half or less of a grid cell) water. When introducing an updated lake representation it is difficult apriori to determine the additional value gained through doing so. There are two key factors here:
\begin{itemize}
	\item Are the updated fields closer to reality?
	\item Do the updated fields increase the accuracy of the model predictions?
\end{itemize}
The first point is straightforward; we want our parametrisation fields to better represent reality. If the lake depth of some lake is updated from 10m to 100m we want to be sure that 100m is closer to the true depth of the lake. For the second point, even if the updated fields are accurate, are they informative in the sense that they enable us to make more accurate predictions? For instance, the main target of lake parametrization is to reproduce lake surface water temperatures (and therefore evaporation rates). If a lake parametrisation scheme is updated to better represent different types of inland waterbodies, the time variability of inland waterbodies and/or the lake morphology fields use more in situ measurements, does this additional information allow for more accurate predictions of the lake surface water temperatures? Is it therefore worthwhile to update the parametrisation in this way? Since the resulting updated fields are ultimately used operationally, it is essential to ensure the accuracy of the fields and prevent any potential degradation or instability of the model. This problem of quickly and automatically verifying the accuracy and information gain of updated lake parametrisations is the aim of this work. \newline

>>>>

\noindent It is a continuous enterprise to update the lake parametrization schemes and their input data fields to better represent small-scale surface processes. It is however challenging to accurately represent lakes in these parametrisations; the majority of lakes which are resolved at a 9km grid spacing have not had their morphology accurately measured, let alone monitored, whilst 28.9$\%$ of land and coastal cells are treated for sub-grid (i.e. covering half or less of a grid cell) water. When introducing an updated lake representation it is difficult apriori to determine the additional value gained through doing so. There are two key factors here:
\begin{itemize}
	\item Are the updated fields closer to reality?
	\item Do the updated fields increase the accuracy of the model predictions?
\end{itemize}
\textcolor{red}{The first point is straightforward; we want our parametrisation fields to better represent reality. If the lake depth of some lake is updated from 10m to 100m we want to be sure that 100m is closer to the true depth of the lake. For the second point, even if the updated fields are accurate, are they informative in the sense that they enable us to make more accurate predictions? For instance, the main target of lake parametrization is to reproduce lake surface water temperatures (and therefore evaporation rates). If a lake parametrisation scheme is updated to better represent different types of inland waterbodies, the time variability of inland waterbodies and/or the lake morphology fields use more in situ measurements, does this additional information allow for more accurate predictions of the lake surface water temperatures? Is it therefore worthwhile to update the parametrisation in this way? Since the resulting updated fields are ultimately used operationally, it is essential to ensure the accuracy of the fields and prevent any potential degradation or instability of the model. This problem of quickly and automatically verifying the accuracy and information gain of updated lake parametrisations is the aim of this work.} \newline
